### 2024-08-29 actuarial.qmd
20240829 - media examples

Using the judgment method of prediction, all gathered information is collected and formulated into a prediction in the person's mind.
The person selects, measures, and combines information and produces projections solely according to their experience and judgment.
For instance, a proclaimed "fantasy expert" might use their experience, expertise, and judgment to make a prediction about how each player will perform by using whatever information and data they deem to be important, aggregating all of this information in their mind to make the prediction for each player.

@@

>>>>

Using the judgment method of prediction, all gathered information is collected and formulated into a prediction in the person's mind.
The person selects, measures, and combines information and produces projections solely according to their experience and judgment.
For instance, a proclaimed "fantasy expert" might use their experience, expertise, and judgment to make a prediction about how each player will perform by using whatever information and data they deem to be important, aggregating all of this information in their mind to make the prediction for each player.
Professional scouts and coaches use judgment when making predictions or selecting players based on their impressions of the players [@DenHartigh2018].
As an example in popular media, in the movie, "Trouble with the Curve", a professional scout makes a judgment about how well a baseball hitter will do in the major leagues from his impressions of the hitter's ability based on the sound of the ball off the player's bat.

@@

As an example of using the actuarial approach, Billy Beane, who was the general manager of the Oakland Athletics at the time, wanted to find ways for his team—which had less finanical resources than its competitors—to compete with teams that hard more money to sign players.
Because the team did not have the resources to sign the best players, they had to find to find other ways to find the optimal players that they could afford.
So, he used statistical formulas that weight variables, such as on-base percentage and slugging percentage, according to their value for winning games, for the use of selecting players.
His approach became well-known based on the Michael Lewis book, "Moneyball: The Art of Winning an Unfair Game", and the eventual movie, "Moneyball".
